### 2018-02-05 Maths Notes/Further Pure/FP2/Further Complex Numbers/Further Complex Numbers.tex
Notes update

>>>>

\section{Solving complex equations}
For any complex number, we generally define the argument to be between $-\pi$ and $\pi$. However we can add multiples of $2\pi$ to the argument to get equivalent answers.\\
\\
We shall use this fact to find all solutions to complex equations.\\
\\
Note: The number of solutions is equal to the order of the equation.
\subsection{Example}
\textit{Solve:}\\
$z^5=i$
$$r=1 \quad \theta=\frac{\theta}{2}$$
$$z^5=\cos(\frac{\pi}{2}+2k\pi)+i\sin(\frac{\pi}{2}+2k\pi)$$
$$z=\cos\Bigg(\frac{\frac{\pi}{2}+2k\pi}{5}
\Bigg)+i\sin\Bigg(\frac{\frac{\pi}{2}+2k\pi}{5}\Bigg)$$
5 Solutions: k=-2,-1,0,1,2\\
$k=-2 \quad z=-0.588-0.809i$\\
$k=-1 \quad z=0.588-0.809i$\\
$k=0 \quad z=0.951+0.309i$\\
$k=1 \quad z=i$\\
$k=2 \quad z=-0.951+0.309i$
